R Notebook

### 2018-09-18 study2/cog-model-discrete-predictions.Rmd
refactored, working

source("../../study1/vacc_import_data.R")
source("../../Scripts/gmod_tools.R")
# source("../../Scripts/virtualEvidence.R")

@@

source("cog-model-main.R")
```

>>>>

source("../study1/vacc_import_data.R", chdir = TRUE)
source("../scripts/gmod_tools.R")
# source("../../Scripts/virtualEvidence.R")

@@

source("../scripts/custom-structure-learning/cog-model-main.R", chdir = TRUE)
```

### 2018-09-18 study2/lab_pres_nb_2018-6-11.Rmd
refactored, working

```{r load in existing objects, message=FALSE, warning=FALSE}
net.struct <- readRDS("net-struct-cogsci2018.rds")

source("../study1/vacc_import_data.R")
source("../Scripts/gmod_tools.R")
source("../Scripts/virtualEvidence.R")

@@

```{r load and tidy study 3 data, include = F}
# load data
d_all <- read.csv("data/study3_data.csv")

>>>>

```{r load in existing objects, message=FALSE, warning=FALSE}
# net.struct <- readRDS("net-struct-cogsci2018.rds")

source("../study1/vacc_import_data.R")
source("../scripts/gmod_tools.R")
source("../scripts/virtualEvidence.R")

@@

```{r load and tidy study 3 data, include = F}
# load data
d_all <- read.csv("../data/study2_data.csv")

### 2018-09-18 study2/study2-evid-ratio.Rmd
refactored, working

>>>>

# maximum likelihood estimate with optim()

WE can do this with optim too, which will work better when we go to do it 14 times.

```{r}
inv_logit <- plogis
logit <- qlogis

evid_score_func <- function(data, par) {
  pred_y <- with(data,
                 {
                   inv_logit(logit(pre) + evid*par[2] + par[1])
                 }
       )
  pred_beta_A <- pred_y * par[3]
  pred_beta_B <- (1-pred_y) * par[3]

  ll <- -1 * sum(dbeta(data$post, pred_beta_A, pred_beta_B, log=TRUE)) # beta regression
  return(ll)
}

result <- optim(par = c(0, 0, 5), fn = evid_score_func, data = d, method="BFGS")

result
```
